---
title: "CCBR XXXX: Your project Title"
title-block-banner: true
subtitle: "This is the subtitle"
author:
  - name: Samarth Mathur
    orcid: 0000-0002-6446-5718
    email: samarth.mathur@nih.gov
    url: https://github.com/samarth8392
    affiliations: 
      - name: "CCR Collaborative Bioinformatics Resource, Office of Science and Technology Resources, National Cancer Institute, National Institutes of Health, Bethesda, MD, USA"
        url: https://bioinformatics.ccr.cancer.gov/ccbr/
      - name: "Advanced Biomedical Computational Science, Frederick National Laboratory for Cancer Research, Frederick, MD 21702, USA"
        url: https://frederick.cancer.gov/research-technology/science-areas/bioinformatics-and-computational-science/advanced-biomedical-computational-science
date: today
format:
  html:
    code-fold: true
    code-tools: true
    code-line-numbers: true
    embed-resources: true
    toc: true
    df-print: paged
    toc-depth: 4
    toc-location: body
    toc-title: "Table of Contents"
    page-layout: full
    theme: default
    css: 
      - "../../_extensions/ccbr-themes/resources/css/html_post_styles.css"
      - "../../_extensions/ccbr-themes/resources/css/author_affiliation.css"
      - "../../_extensions/ccbr-themes/resources/css/buttons.css"
      - "../../_extensions/ccbr-themes/resources/fontawesome/css/all.min.css"
    grid:
      margin-width: 250px
params:
  workdir: ""
  outdir: ""
  resources: ""
---

```{r echo=FALSE, results='asis'}
cat('<span class="last-modified">📝 Last modified:', format(Sys.Date(), "%m-%d-%Y"), '</span>')
```

# Header 1
## Header 2
### Header 3
#### Header 4

---

# Specialized buttons

<!-- Filled Buttons -->
[View Repository](https://github.com/user/repo){.btn-github}
[CCBR](https://github.com/CCBR){.btn-sitemap}
[OneDrive Folder](https://onedrive.com/folder){.btn-onedrive}
[Google Drive](https://drive.google.com/folder){.btn-gdrive}
[Dropbox Files](https://dropbox.com/folder){.btn-dropbox}
[LinkedIn Profile](https://linkedin.com/in/user){.btn-linkedin}
[Follow on X](https://twitter.com/user){.btn-twitter}
[Join Slack](https://slack.com/invite){.btn-slack}
[Discord Server](https://discord.gg/invite){.btn-discord}
[YouTube Channel](https://youtube.com/@channel){.btn-youtube}
[Email Us](mailto:user@email.com){.btn-email}
[Documentation](https://docs.example.com){.btn-docs}
[Download File](files/data.zip){.btn-download}
[Download PDF](files/document.pdf){.btn-pdf}

[GitHub (Outline)](https://github.com/user/repo){.btn-outline-github}
[OneDrive (Outline)](https://onedrive.com/folder){.btn-outline-onedrive}


#### Button Groups
<!-- Button Groups (multiple buttons together) -->
::: {.btn-group}
[GitHub](https://github.com){.btn-github}
[Docs](https://docs.com){.btn-docs}
[Download](files/data.zip){.btn-download}
:::


# Regular Buttons


[Download Report](link-url){.btn-primary}
[View Results](link-url){.btn-primary}

[GitHub Repository](link-url){.btn-secondary}
[Documentation](link-url){.btn-secondary}


[Important Link](link-url){.btn-accent}
[Get Started](link-url){.btn-accent}

[Learn More](link-url){.btn-outline-primary}
[Contact Us](link-url){.btn-outline-secondary}

[Quick Link](link-url){.btn-pill}
[Tag Style](link-url){.btn-pill}

#### Icon buttons

[🔗](link-url){.btn-icon}
[📊](link-url){.btn-icon}
[📁](link-url){.btn-icon}


#### Button Group

::: {.btn-group}
[Primary Action](link1){.btn-primary}
[Secondary Action](link2){.btn-outline-primary}
[More Info](link3){.btn-pill}
:::

[primary](link-url){.btn-outline-primary}
[light](link-url){.btn-outline-light}
[soft](link-url){.btn-outline-soft}
[pastel](link-url){.btn-outline-pastel}
[mint](link-url){.btn-outline-mint}

# Data Visualization (in Tabs) Examples

::: {.panel-tabset .theme-ccbr-poppy}

## Scatter Plot

```{r}
# Generate random data
set.seed(123)
x <- runif(10, 0, 10)
y <- runif(10, 0, 10)

# Create scatter plot
plot(x, y, 
     pch = 16, 
     col = "#4e9db5", 
     cex = 1.5,
     main = "Random Scatter Plot",
     xlab = "X values", 
     ylab = "Y values")
```

## Bar Plot

```{r}
# Sample data
categories <- c("A", "B", "C", "D", "E")
values <- c(23, 17, 35, 29, 12)

# Create bar plot
barplot(values, 
        names.arg = categories,
        col = "#7cc349",
        main = "Category Comparison",
        xlab = "Categories", 
        ylab = "Values",
        border = "#528230")
```

## Pie Chart

```{r}
# Data for pie chart
labels <- c("Research", "Analysis", "Writing", "Review")
sizes <- c(35, 25, 25, 15)
colors <- c("#4e9db5", "#7cc349", "#ecba4c", "#296b7f")

# Create pie chart
pie(sizes, 
    labels = labels, 
    col = colors,
    main = "Project Time Distribution")
```

:::

## Different Base R Styles

::: {.panel-tabset .theme-ccbr-scientific}

## Enhanced Scatter

```{r}
# Random data with grid
set.seed(789)
x <- runif(10, 1, 8)
y <- runif(10, 2, 9)

# Enhanced scatter plot
plot(x, y, 
     pch = 19, 
     col = "#296b7f", 
     cex = 2,
     main = "Enhanced Scatter Plot",
     xlab = "X values", 
     ylab = "Y values",
     xlim = c(0, 10),
     ylim = c(0, 10))
grid(col = "gray", lty = "dotted")
```

## Horizontal Bar

```{r}
# Data for horizontal bars
items <- c("Item A", "Item B", "Item C", "Item D")
counts <- c(15, 28, 22, 19)

# Horizontal barplot
barplot(counts, 
        names.arg = items,
        horiz = TRUE,
        col = "#7cc349",
        main = "Horizontal Bar Chart",
        xlab = "Count",
        border = "#528230")
```

## Donut-style Pie

```{r}
# Simple data
activity <- c("Coding", "Testing", "Documentation", "Meetings")
time <- c(40, 20, 25, 15)
colors <- c("#4e9db5", "#7cc349", "#ecba4c", "#19424e")

# Create pie chart
pie(time, 
    labels = paste(activity, "(", time, "%)", sep = ""), 
    col = colors,
    main = "Time Allocation",
    clockwise = TRUE)
```

:::

## More Base R Variations

::: {.panel-tabset .theme-ccbr-gradient}

## Line + Points

```{r}
# Time series style data
set.seed(999)
time <- 1:10
values <- cumsum(rnorm(10, 0.5, 1))

# Line plot with points
plot(time, values, 
     type = "b",
     pch = 16,
     col = "#296b7f",
     lwd = 2,
     main = "Trend Over Time",
     xlab = "Time Point",
     ylab = "Cumulative Value")
```

## Stacked Bar

```{r}
# Matrix for stacked bars
data_matrix <- matrix(c(12, 8, 15, 
                       18, 12, 10, 
                       10, 15, 20), 
                     nrow = 3, byrow = TRUE)
colnames(data_matrix) <- c("Group A", "Group B", "Group C")
rownames(data_matrix) <- c("Category 1", "Category 2", "Category 3")

# Stacked barplot
barplot(data_matrix, 
        col = c("#4e9db5", "#7cc349", "#ecba4c"),
        main = "Stacked Bar Chart",
        xlab = "Groups",
        ylab = "Values",
        legend.text = TRUE)
```

## Multi Pie

```{r}
# Split plotting area for multiple pies
par(mfrow = c(1, 2))

# First pie
pie1 <- c(30, 70)
pie(pie1, 
    labels = c("Yes", "No"), 
    col = c("#7cc349", "#ecba4c"),
    main = "Survey A")

# Second pie  
pie2 <- c(45, 55)
pie(pie2, 
    labels = c("Pass", "Fail"), 
    col = c("#4e9db5", "#296b7f"),
    main = "Survey B")
```

:::

#### Back to Top button

::: {style="text-align: center; margin: 2em 0;"}
[Back to Top](#){.btn-outline-light}
:::

#### Footer

::: {.ccbr-footer}
Created by **Samarth Mathur, PhD** • NIH/NCI/CCR/CCBR

[GitHub](https://github.com/samarth8392){.btn-outline-github .btn-sm}
[Documentation](https://samarth8392.github.io/ccbr-themes){.btn-outline-docs .btn-sm}
[Email](mailto:samarth.mathur@nih.gov){.btn-outline-email .btn-sm}
[CCBR](https://samarth8392.github.io/ccbr-themes){.btn-outline-sitemap .btn-sm}
:::